---
title: "AUDPC and yield correlations"
author: "Erik Delaquis"
date: "4/10/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Libraries, message=FALSE, warning=FALSE}
#Libraries
library(tidyverse)
library(ggrepel)
library(readxl)
library(agricolae)
```

# Y1

```{r message=FALSE, warning=FALSE}
#Leaving here just in case we want to go back to disaggregating sites


#Y1
#Filter only site 1
Y1_S1 <- read_excel("data/3Y_for_ANOVA.xlsx",
                    sheet = "Y1") %>% filter(Site == 1)
Y1_S1
DAP <- c(60, 150, 270)
ratings <-
  as.data.frame(Y1_S1[, c(9, 10, 11)]) #Have to transform into data frame for the next step to work
ratings

#Calculate absolute and relative AUDPC ratings and bind them on the end of the data set
audpc.abs.Y1_S1 <-
  audpc(ratings, DAP, type = "absolute") #Absolute AUDPC for ANOVA purposes
Y1_S1.AUDPC <-
  cbind(Y1_S1, audpc.abs.Y1_S1) %>% rename(audpc_absolute = audpc.abs.Y1_S1)

audpc.rel.Y1_S1 <- audpc(ratings, DAP, type = "relative")
Y1_S1.AUDPC <-
  cbind(Y1_S1.AUDPC, audpc.rel.Y1_S1) %>% rename(audpc_relative = audpc.rel.Y1_S1)
glimpse(Y1_S1.AUDPC)

#Filter site 2
Y1_S2 <- read_excel("data/3Y_for_ANOVA.xlsx",
                    sheet = "Y1") %>% filter(Site == 2)
Y1_S2
DAP <- c(60, 150, 270)
ratings <-
  as.data.frame(Y1_S2[, c(9, 10, 11)]) #Have to transform into data frame for the next step to work
ratings

#Calculate absolute and relative AUDPC ratings and bind them on the end of the data set
audpc.abs.Y1_S2 <-
  audpc(ratings, DAP, type = "absolute") #Absolute AUDPC for ANOVA purposes
Y1_S2.AUDPC <-
  cbind(Y1_S2, audpc.abs.Y1_S2) %>% rename(audpc_absolute = audpc.abs.Y1_S2)

audpc.rel.Y1_S2 <- audpc(ratings, DAP, type = "relative")
Y1_S2.AUDPC <-
  cbind(Y1_S2.AUDPC, audpc.rel.Y1_S2) %>% rename(audpc_relative = audpc.rel.Y1_S2)
glimpse(Y1_S2.AUDPC)
```

## Processing Y1 data - combining both sites

```{r data prep, message=FALSE, warning=FALSE}
#data prep

#Using the file prepared with all 3 years called 3Y_for_ANOVA
#Load data from excel workbook
Y1 <- read_excel("data/3Y_for_ANOVA.xlsx",
                 sheet = "Y1")
ratings <-
  as.data.frame(Y1[, c(9, 10, 11)]) #Have to transform into data frame for the next step to work
ratings
DAP <- c(60, 150, 270)

audpc.abs.Y1 <-
  audpc(ratings, DAP, type = "absolute") #Absolute AUDPC for ANOVA purposes
Y1.AUDPC <-
  cbind(Y1, audpc.abs.Y1) %>% rename(audpc_absolute = audpc.abs.Y1)

audpc.rel.Y1 <- audpc(ratings, DAP, type = "relative")
Y1.AUDPC <-
  cbind(Y1.AUDPC, audpc.rel.Y1) %>% rename(audpc_relative = audpc.rel.Y1)
glimpse(Y1.AUDPC)
```

### Visualize data

```{r message=FALSE, warning=FALSE}
ggplot(Y1.AUDPC, aes(x = Var, y = audpc_absolute, fill = Split_trt)) +
  geom_boxplot(position = position_dodge(0.8)) +
  geom_dotplot(binaxis = 'y',
               stackdir = 'center',
               position = position_dodge(0.8))

ggplot(Y1.AUDPC, aes(x = Var, y = Adj_yield_kg, fill = Split_trt)) +
  geom_boxplot(position = position_dodge(0.8)) +
  geom_dotplot(binaxis = 'y',
               stackdir = 'center',
               position = position_dodge(0.8))
```

### Line graphs for Y1 (both sites)

```{r message=FALSE, warning=FALSE}
#Make sure to call the Y1.AUDPC from above (chunk starting at line 66)
#library for summarizing
library(doBy)

#First transform combined Y1 data into long format
Y1.AUDPC.gg <-
  Y1.AUDPC %>% select(
    Var,
    Site,
    Rep,
    "60" = Percent_inf_cul_60,
    "150" = Percent_inf_cul_150,
    "270" = Percent_inf_cul_270,
    audpc_absolute,
    audpc_relative
  ) %>%
  gather(DAP, Percent_inf, "60":"270", factor_key = TRUE)

library(gridExtra)
#Both together to allow use of faceting
Y1try <-
  summaryBy(Percent_inf ~ Var + DAP + Site,
            data = Y1.AUDPC.gg,
            FUN = c(length, mean, sd))

# Rename column change.length to just N
names(Y1try)[names(Y1try) == "Percent_inf.length"] <- "N"
# Calculate se for error bars using basic formula of sd/sqrt(N)
Y1try$Percent_inf.se <- Y1try$Percent_inf.sd / sqrt(Y1try$N)

Y1try_line <-
  ggplot(data = Y1try, aes(x = DAP, y = Percent_inf.mean, group = Var)) +
  geom_errorbar(
    aes(
      ymin = Percent_inf.mean - Percent_inf.se,
      ymax = Percent_inf.mean + Percent_inf.se
    ),
    width = .1
  ) +
  geom_line(aes(color = Var), size = 1) + ylim(0, 100) +
  geom_point(aes(color = Var), shape = 1, size = 3) +
  labs(color = 'Variety') +
  theme_classic()

Y1try_line + facet_grid(rows = vars(Site), labeller = label_both) +
  xlab("Days after planting (DAP)") +
  ylab("Percent infection")
```

#### Separating sites

##### Y1 Site 1 no fertilizer (NF)

```{r message=FALSE, warning=FALSE}
Y1.S1.NF <- read_excel("data/3Y_for_ANOVA.xlsx",
                       sheet = "Y1") %>% filter(Site == 1 &
                                                  Split_trt == "Without fertilizer")
DAP <- c(60, 150, 270)
ratings <-
  as.data.frame(Y1.S1.NF[, c(9, 10, 11)]) #Have to transform into data frame for the next step to work
ratings

relative <-
  audpc(ratings, DAP, type = "relative") #Calculating relative AUDPC for correlation with yield, as in the example
relative

correlation(Y1.S1.NF$Adj_yield_kg, relative, method = "kendall")
correlation(Y1.S1.NF$Adj_yield_kg, Y1.S1.NF$Percent_inf_cul_60, method =
              "kendall")
correlation(Y1.S1.NF$Adj_yield_kg, Y1.S1.NF$Percent_inf_cul_150, method =
              "kendall")
correlation(Y1.S1.NF$Adj_yield_kg, Y1.S1.NF$Percent_inf_cul_270, method =
              "kendall")
```

```{r message=FALSE, warning=FALSE}
#Bind calculated absolute AUDPC to original and rename
audpc.Y1.S1.NF <-
  audpc(ratings, DAP, type = "absolute") #Absolute AUDPC for ANOVA purposes
Y1.S1.NF.AUDPC <-
  cbind(Y1.S1.NF, audpc.Y1.S1.NF) %>% rename(audpc = audpc.Y1.S1.NF)
glimpse(Y1.S1.NF.AUDPC)

#ANOVA
Y1.S1.NF.model <-
  lm(audpc ~ Var + Rep + Var * Rep, data = Y1.S1.NF.AUDPC)
Y1.S1.NF.ANOVA <- anova(Y1.S1.NF.model) #ANOVA and print the results
Y1.S1.NF.ANOVA
Y1.S1.NF.aov = aov(Y1.S1.NF.model) #ANOVA and store the data for next use
```

```{r message=FALSE, warning=FALSE}
##Can do post-hoc Tukey HSD with Agricolae package
Y1.S1.NF.TUKEY <- HSD.test(Y1.S1.NF.aov, trt = 'Var')
Y1.S1.NF.TUKEY
plot(Y1.S1.NF.TUKEY) + title(sub = "Site 1, Y1, No fertilizer")

##Can also do Tukey HSD with multcompview package, output graph a little different. See https://www.r-graph-gallery.com/84-tukey-test.html
#library(multcompView)
# Tukey test to study each pair of treatment :
#Y1.S1.NF.TUKEYMult <- TukeyHSD(Y1.S1.NF.aov, "Var", conf.level=0.95)
#Y1.S1.NF.TUKEYMult

# Tukey test representation :
#plot(Y1.S1.NF.TUKEYMult , las=1 , col="brown")
```

##### Y1 Site 1 with fertilizer

```{r message=FALSE, warning=FALSE}
Y1.S1.WF <- read_excel("data/3Y_for_ANOVA.xlsx",
                       sheet = "Y1") %>% filter(Site == 1 &
                                                  Split_trt == "With fertilizer")
DAP <- c(60, 150, 270)
ratings <-
  as.data.frame(Y1.S1.WF[, c(9, 10, 11)]) #Have to transform into data frame for the next step to work
ratings

relative <- audpc(ratings, DAP, type = "relative")
relative
correlation(Y1.S1.WF$Adj_yield_kg, relative, method = "kendall")
```

```{r message=FALSE, warning=FALSE}
#Bind calculated absolute AUDPC to original and rename
audpc.Y1.S1.WF <-
  audpc(ratings, DAP, type = "absolute") #Absolute AUDPC for ANOVA purposes
Y1.S1.WF.AUDPC <-
  cbind(Y1.S1.WF, audpc.Y1.S1.WF) %>% rename(audpc = audpc.Y1.S1.WF)
glimpse(Y1.S1.WF.AUDPC)
#ANOVA
Y1.S1.WF.model <-
  lm(audpc ~ Var + Rep + Var * Rep, data = Y1.S1.WF.AUDPC)
Y1.S1.WF.ANOVA <- anova(Y1.S1.NF.model) #ANOVA and print the results
Y1.S1.WF.ANOVA
Y1.S1.WF.aov = aov(Y1.S1.WF.model) #ANOVA and store the data for next use

##Can do post-hoc Tukey HSD with Agricolae package
Y1.S1.WF.TUKEY <- HSD.test(Y1.S1.WF.aov, trt = 'Var')
Y1.S1.WF.TUKEY
plot(Y1.S1.WF.TUKEY) + title(sub = "Site 1, Y1, With fertilizer")
```

##### Y1 Site 2, Without fertilizer

```{r message=FALSE, warning=FALSE}
Y1.S2.NF <- read_excel("data/3Y_for_ANOVA.xlsx",
                       sheet = "Y1") %>% filter(Site == 2 &
                                                  Split_trt == "Without fertilizer")
DAP <- c(60, 150, 270)
ratings <-
  as.data.frame(Y1.S2.NF[, c(9, 10, 11)]) #Have to transform into data frame for the next step to work
ratings

relative <- audpc(ratings, DAP, type = "relative")
relative
correlation(Y1.S2.NF$Adj_yield_kg, relative, method = "kendall")
```

```{r message=FALSE, warning=FALSE}
#Bind calculated absolute AUDPC to original and rename
audpc.Y1.S2.NF <-
  audpc(ratings, DAP, type = "absolute") #Absolute AUDPC for ANOVA purposes
Y1.S2.NF.AUDPC <-
  cbind(Y1.S2.NF, audpc.Y1.S2.NF) %>% rename(audpc = audpc.Y1.S2.NF)
glimpse(Y1.S2.NF.AUDPC)
#ANOVA
Y1.S2.NF.model <-
  lm(audpc ~ Var + Rep + Var * Rep, data = Y1.S2.NF.AUDPC)
Y1.S2.NF.ANOVA <- anova(Y1.S2.NF.model) #ANOVA and print the results
Y1.S2.NF.ANOVA
Y1.S2.NF.aov = aov(Y1.S2.NF.model) #ANOVA and store the data for next use

##Can do post-hoc Tukey HSD with Agricolae package
Y1.S2.NF.TUKEY <- HSD.test(Y1.S2.NF.aov, trt = 'Var')
Y1.S2.NF.TUKEY
plot(Y1.S2.NF.TUKEY) + title(sub = "Site 2, Y1, No fertilizer")
```

##### Y1 Site 2, With fertilizer

```{r message=FALSE, warning=FALSE}
Y1.S2.WF <- read_excel("data/3Y_for_ANOVA.xlsx",
                       sheet = "Y1") %>% filter(Site == 2 &
                                                  Split_trt == "With fertilizer")
DAP <- c(60, 150, 270)
ratings <-
  as.data.frame(Y1.S2.WF[, c(9, 10, 11)]) #Have to transform into data frame for the next step to work
ratings

relative <- audpc(ratings, DAP, type = "relative")
relative
correlation(Y1.S2.WF$Adj_yield_kg, relative, method = "kendall")
```

```{r message=FALSE, warning=FALSE}
#Bind calculated absolute AUDPC to original and rename
audpc.Y1.S2.WF <-
  audpc(ratings, DAP, type = "absolute") #Absolute AUDPC for ANOVA purposes
Y1.S2.WF.AUDPC <-
  cbind(Y1.S2.WF, audpc.Y1.S2.WF) %>% rename(audpc = audpc.Y1.S2.WF)
glimpse(Y1.S2.WF.AUDPC)
#ANOVA
Y1.S2.WF.model <-
  lm(audpc ~ Var + Rep + Var * Rep, data = Y1.S2.WF.AUDPC)
Y1.S2.WF.ANOVA <- anova(Y1.S2.WF.model) #ANOVA and print the results
Y1.S2.WF.ANOVA
Y1.S2.WF.aov = aov(Y1.S2.WF.model) #ANOVA and store the data for next use

##Can do post-hoc Tukey HSD with Agricolae package
Y1.S2.WF.TUKEY <- HSD.test(Y1.S2.WF.aov, trt = 'Var')
Y1.S2.WF.TUKEY
plot(Y1.S2.WF.TUKEY) + title(sub = "Site 2, Y1, With fertilizer")
```

## Y2

### All data

```{r message=FALSE, warning=FALSE}
#data prep
Y2 <- read_excel("data/3Y_for_ANOVA.xlsx",
                 sheet = "Y2")
DAP <- c(60, 150, 270)
ratings <-
  as.data.frame(Y2[, c(10, 11, 12)]) #Have to transform into data frame for the next step to work
ratings

relative <- audpc(ratings, DAP, type = "relative")
relative
correlation(Y2$Adj_yield_kg, relative, method = "kendall")

#Absolute and relative AUDPC and cbind to dataframe
audpc.abs.Y2 <-
  audpc(ratings, DAP, type = "absolute") #Absolute AUDPC for ANOVA purposes
Y2.AUDPC <-
  cbind(Y2, audpc.abs.Y2) %>% rename(audpc_absolute = audpc.abs.Y2)

audpc.rel.Y2 <- audpc(ratings, DAP, type = "relative")
Y2.AUDPC <-
  cbind(Y2.AUDPC, audpc.rel.Y2) %>% rename(audpc_relative = audpc.rel.Y2)
glimpse(Y2.AUDPC)

Y2.AUDPC$Var = as.factor(Y2.AUDPC$Var)
Y2.AUDPC$Split_trt = as.factor(Y2.AUDPC$Split_trt)
```

#### Visualize data

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Y2.AUDPC, aes(x = Var, y = audpc_absolute, fill = Split_trt)) +
  geom_boxplot(position = position_dodge(0.8)) +
  geom_dotplot(binaxis = 'y',
               stackdir = 'center',
               position = position_dodge(0.8))

ggplot(Y2.AUDPC, aes(x = Var, y = Adj_yield_kg, fill = Split_trt)) +
  geom_boxplot(position = position_dodge(0.8)) +
  geom_dotplot(binaxis = 'y',
               stackdir = 'center',
               position = position_dodge(0.8))
```

#### Correlation

```{r echo=FALSE, message=FALSE, warning=FALSE}
correlation(Y2.AUDPC$Adj_yield_kg, Y2.AUDPC$audpc_absolute, method = "kendall")
#correlation(Y2.AUDPC$Adj_yield_kg, Y2.AUDPC$Percent_inf_cul_60, method="kendall")
#correlation(Y2.AUDPC$Adj_yield_kg, Y2.AUDPC$Percent_inf_cul_150, method="kendall")
#correlation(Y2.AUDPC$Adj_yield_kg, Y2.AUDPC$Percent_inf_cul_270, method="kendall")
```

```{r echo=FALSE, include=FALSE}
#ANOVA
Y2.model <- lm(audpc_absolute ~ Var + Rep + Var * Rep, data = Y2.AUDPC)
Y2.ANOVA <- anova(Y2.model) #ANOVA and print the results
Y2.ANOVA
Y2.aov = aov(Y2.model) #ANOVA and store the data for next use

##Can do post-hoc Tukey HSD with Agricolae package
Y2.TUKEY <- HSD.test(Y2.aov, trt = 'Var')
Y2.TUKEY
plot(Y2.TUKEY) + title(sub = "Y2")
```

```{r echo=FALSE, include=FALSE}
#Another version of agricolae split plot
attach(Y2)
Variety = factor(Var)
Block = factor(Rep)
Seed = factor(Split_trt)

sp.plot(Block, Variety, Seed, Adj_yield_kg)
```

## Y3

### All data

```{r include=FALSE, warning=FALSE}
#data prep
Y3 <- read_excel("data/3Y_for_ANOVA.xlsx",
                 sheet = "Y3")
DAP <- c(30, 60, 150, 270)
ratings <-
  as.data.frame(Y3[, c(6, 10, 11, 12)]) #Have to transform into data frame for the next step to work
ratings

relative <- audpc(ratings, DAP, type = "relative")
relative
correlation(Y3$Adj_yield_kg, relative, method = "kendall")

#Absolute and relative AUDPC and cbind to dataframe
audpc.abs.Y3 <-
  audpc(ratings, DAP, type = "absolute") #Absolute AUDPC for ANOVA purposes
Y3.AUDPC <-
  cbind(Y3, audpc.abs.Y3) %>% rename(audpc_absolute = audpc.abs.Y3)

audpc.rel.Y3 <- audpc(ratings, DAP, type = "relative")
Y3.AUDPC <-
  cbind(Y3.AUDPC, audpc.rel.Y3) %>% rename(audpc_relative = audpc.rel.Y3)
glimpse(Y3.AUDPC)

Y3.AUDPC$Var = as.factor(Y3.AUDPC$Var)
Y3.AUDPC$Split_trt = as.factor(Y3.AUDPC$Split_trt)
```

##### Visualize data

```{r message=FALSE, warning=FALSE}
ggplot(Y3.AUDPC, aes(x = Var, y = audpc_absolute, fill = Split_trt)) +
  geom_boxplot(position = position_dodge(0.8)) +
  geom_dotplot(binaxis = 'y',
               stackdir = 'center',
               position = position_dodge(0.8))

ggplot(Y3.AUDPC, aes(x = Var, y = Adj_yield_kg, fill = Split_trt)) +
  geom_boxplot(position = position_dodge(0.8)) +
  geom_dotplot(binaxis = 'y',
               stackdir = 'center',
               position = position_dodge(0.8))
```

##### Correlation

```{r message=FALSE, warning=FALSE}
correlation(Y3$Adj_yield_kg, Y3$Percent_inf_30, method = "kendall")
#correlation(Y3$Adj_yield_kg, Y3$Percent_inf_cul_60, method="kendall")
#correlation(Y3$Adj_yield_kg, Y3$Percent_inf_cul_150, method="kendall")
#correlation(Y3$Adj_yield_kg, Y3$Percent_inf_cul_270, method="kendall")
```

```{r message=FALSE, warning=FALSE}
#ANOVA
Y3.model <- lm(audpc_absolute ~ Var + Rep + Var * Rep, data = Y3.AUDPC)
Y3.ANOVA <- anova(Y3.model) #ANOVA and print the results
Y3.ANOVA
Y3.aov = aov(Y3.model) #ANOVA and store the data for next use

##Can do post-hoc Tukey HSD with Agricolae package
Y3.TUKEY <- HSD.test(Y3.aov, trt = 'Var')
Y3.TUKEY
plot(Y3.TUKEY) + title(sub = "Y3")
```

# Correlation graphs

We'll use the ggpubr package, which includes a number of convenient functions for easy, publication ready graphs and figures. We'll use make a few versions and a multiplot with parts a,b,c for the three years.

```{r message=FALSE, warning=FALSE}
#Easy publication ready graphs with ggpubr
library(ggpubr)
```

```{r message=FALSE, warning=FALSE}
ggplot(Y1.AUDPC,
       aes(x = audpc_relative, y = Adj_yield_kg, color = factor(Site))) +
  geom_point(alpha = 0.7) +
  stat_smooth(
    aes(color = factor(Site)),
    method = lm,
    se = TRUE,
    formula = y ~ x
  ) +
  theme_classic() +
  labs(x = "rAUDPC", y = bquote('Yield' ~ (t ~ ha ^ -1))) +
  scale_colour_discrete("Site") +
  stat_cor(aes(color = factor(Site)),
           label.x = 0.4,
           show.legend = FALSE) +
  stat_regline_equation(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                        show.legend = FALSE,
                        formula = y ~ x)
```

```{r message=FALSE, warning=FALSE}
#Y2
#All together
ggplot(Y2.AUDPC, aes(x = audpc_relative, y = Adj_yield_kg)) +
  geom_point(alpha = 0.7, aes(color = Split_trt)) +
  stat_smooth(method = lm,
              se = TRUE,
              formula = y ~ x) +
  theme_classic() +
  labs(x = "rAUDPC", y = bquote('Yield' ~ (t ~ ha ^ -1))) +
  scale_colour_discrete("Seed class") +
  stat_cor(label.x = 0.25, label.y = 16) +
  stat_regline_equation(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), label.x =
                          0.25, label.y = 12) +
  ylim(0, 70)
```

```{r message=FALSE, warning=FALSE}
#Y2
ggplot(Y2.AUDPC,
       aes(x = audpc_relative, y = Adj_yield_kg, color = Split_trt)) +
  geom_point(alpha = 0.7, aes(color = Split_trt)) +
  stat_smooth(method = lm,
              se = FALSE,
              formula = y ~ x) +
  theme_classic() +
  labs(x = "rAUDPC", y = bquote('Yield (t ha' ~ (ha ^ -1))) +
  scale_colour_discrete("Seed class") +
  stat_cor(label.x = 0.75,
           label.y = c(6, 3, 0),
           show.legend = FALSE) +
  stat_regline_equation(
    aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
    label.x = 0.4,
    label.y = c(6, 3, 0),
    show.legend = FALSE
  ) +
  ylim(0, 70)
```

```{r message=FALSE, warning=FALSE}
#Y3
ggplot(Y3.AUDPC, aes(x = audpc_relative, y = Adj_yield_kg)) +
  geom_point(alpha = 0.7, aes(color = Split_trt)) +
  stat_smooth(method = lm,
              se = TRUE,
              formula = y ~ x) +
  theme_classic() +
  labs(x = "rAUDPC", y = bquote('Yield' ~ (t ~ ha ^ -1))) +
  scale_colour_discrete("Seed class") +
  stat_cor(label.x = 0.25, label.y = 20) +
  stat_regline_equation(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~")), label.x =
                          0.25, label.y = 16) +
  ylim(0, 70)
```

We'll use cowplot to patch the three together into a multiplot

```{r warning=FALSE, message=FALSE}
library(cowplot)

#Calling plots from years 2 and 3 again
Y2 <- ggplot(Y2.AUDPC, aes(x = audpc_relative, y = Adj_yield_kg)) +
  geom_point(alpha = 0.7, aes(color = Split_trt)) +
  stat_smooth(method = lm,
              se = TRUE,
              formula = y ~ x) +
  theme_classic() +
  labs(x = "rAUDPC", y = bquote('Yield' ~ (t ~ ha ^ -1))) +
  scale_colour_discrete("Seed class") +
  stat_cor(label.x = 0.2, label.y = 16) +
  stat_regline_equation(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), label.x =
                          0.2, label.y = 10) +
  ylim(0, 70)

Y3 <- ggplot(Y3.AUDPC, aes(x = audpc_relative, y = Adj_yield_kg)) +
  geom_point(alpha = 0.7, aes(color = Split_trt)) +
  stat_smooth(method = lm,
              se = TRUE,
              formula = y ~ x) +
  theme_classic() +
  labs(x = "rAUDPC", y = bquote('Yield' ~ (t ~ ha ^ -1))) +
  scale_colour_discrete("Seed class") +
  stat_cor(label.x = 0.2, label.y = 16) +
  stat_regline_equation(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~")), label.x =
                          0.2, label.y = 10) +
  ylim(0, 70) + ylab(NULL)
```

Now we'll use cowplot to make our multi-part figure. because of the complex arrangement we want, we will need to make 2 grid plots using by nesting calls.

```{r message=FALSE, warning=FALSE}
#Aligning plots for the bottom row (years 2 and 3)
#Remove legend to line up axes well
hi <-
  plot_grid(
    Y2 + theme(legend.position = "none"),
    Y3 + theme(legend.position = "none"),
    align = 'h',
    labels = c("B", "C") #Add labels - this will be bottom row
  )

#This is cowplot code for extracting the common legend - because the legend is the same for both years we can select either one
hileg <- get_legend(Y2 + theme(legend.position = "bottom"))

#Plot the 2 parts from the same row combined and the legend
bottom <- plot_grid(hi, hileg, ncol = 1, rel_heights = c(1, .1))

#Now make the top row
top <-
  ggplot(Y1.AUDPC,
         aes(x = audpc_relative, y = Adj_yield_kg, color = factor(Site))) +
  geom_point(alpha = 0.7) +
  stat_smooth(
    aes(color = factor(Site)),
    method = lm,
    se = TRUE,
    formula = y ~ x
  ) +
  theme_classic() + theme(
    legend.position = c(0.95, 0.8),
    legend.background = element_rect(fill = "white", color = "black")
  ) +
  labs(x = "rAUDPC", y = bquote('Yield' ~ (t ~ ha ^ -1))) +
  scale_colour_discrete("Site") +
  stat_cor(
    aes(color = factor(Site)),
    label.x = 0.4,
    label.y = c(55, 59),
    show.legend = FALSE
  ) +
  stat_regline_equation(
    aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
    label.y = c(55, 59),
    show.legend = FALSE,
    formula = y ~ x
  )

#Now align all 3 using a second multiplot call
plot_grid(top , bottom, labels = c('A', ' '), ncol = 1)

#Save the result
ggsave(
  "Combined_reg.tiff",
  height = 170,
  width = 178,
  units = "mm",
  dpi = 300
)
```

## Extra If we still feel like exploring, below are some other ways to visualize
```{r message=FALSE, warning=FALSE}
#Y3
#Individual
ggplot(Y3.AUDPC,
       aes(x = audpc_relative, y = Adj_yield_kg, color = Split_trt)) +
  geom_point(alpha = 0.7, aes(color = Split_trt)) +
  stat_smooth(method = lm,
              se = FALSE,
              formula = y ~ x) +
  theme_classic() +
  labs(x = "rAUDPC", y = bquote('Yield (t ha' ~ (ha ^ -1))) +
  scale_colour_discrete("Seed class") +
  stat_cor(
    label.x = 0.5,
    sep = "~~~",
    label.y = c(6, 3, 0),
    show.legend = FALSE
  ) +
  stat_regline_equation(
    aes(label = paste(..eq.label.., ..rr.label.., sep = "~~")),
    label.x = 0.2,
    label.y = c(6, 3, 0),
    show.legend = FALSE
  ) +
  ylim(0, 70)
```

### Using ggscatter and adding rug plot
```{r message=FALSE, warning=FALSE}
ggscatter(Y3.AUDPC,
          x = "audpc_relative",
          y = "Adj_yield_kg",
          add = "reg.line") +
  #stat_smooth(method=lm, se=TRUE, formula = y ~ x)+
  #stat_smooth(data=Y2.AUDPC, aes(color=Split_trt), method=lm, se=FALSE, formula = y ~ x)+
  geom_rug(sides = "bl", size = 0.75, aes(color = Split_trt)) + #tblr gives sides of the plot to put rug on
  theme_classic() +
  labs(x = "rAUDPC", y = bquote('Yield (t ha' ~ (ha ^ -1))) +
  scale_colour_discrete("Seed class") +
  stat_cor(label.x = 0.25, label.y = 20) +
  stat_regline_equation(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), label.x =
                          0.25, label.y = 16) +
  ylim(0, 70)

ggscatterhist(
  Y2.AUDPC,
  x = "audpc_relative",
  y = "Adj_yield_kg",
  add = "reg.line",
  margin.plot = "histogram",
  # I'd suggest removing this line to get density plots
  margin.params = list(fill = "Split_trt", color = "black", size = 0.2)
) + stat_cor(label.x = 0.25, label.y = 20) +
  stat_regline_equation(label.x = 0.25, label.y = 18)

ggscatterhist(
  Y3.AUDPC,
  x = "audpc_relative",
  y = "Adj_yield_kg",
  add = "reg.line",
  margin.plot = "histogram",
  # I'd suggest removing this line to get density plots
  margin.params = list(fill = "Split_trt", color = "black", size = 0.2)
)
```

### Making density plots
```{r message=FALSE, warning=FALSE}
ggplot(Y2.AUDPC,
       aes(x = audpc_relative, y = Adj_yield_kg, color = Split_trt)) +
  geom_point() +
  stat_density_2d(aes(alpha = ..piece..)) +
  theme_classic2() +
  guides(color = FALSE, alpha = FALSE) +
  labs(x = "rAUDPC", y = bquote('Yield (t ha' ~ (ha ^ -1)))

ggplot(Y3.AUDPC,
       aes(x = audpc_relative, y = Adj_yield_kg, color = Split_trt)) +
  stat_density_2d(aes(alpha = ..piece..)) +
  theme_classic2() +
  guides(color = FALSE, alpha = FALSE) +
  labs(x = "rAUDPC", y = bquote('Yield (t ha' ~ (ha ^ -1)))
```

## Citation for the agricolae package
```{r warning=FALSE, message=FALSE}
citation(package = "agricolae")
```
